Maximizing Ink in Symmetric Partial Edge Drawings of $k$-plane Graphs

### 2018-01-09 eurocg/paper.tex
formatting
Korrekturen von Michael

The \emph{intersection graph} $ C = (V,E) $ of $ \Gamma $ is the graph containing a vertex $v_i$ in $ V $ for every $ s_i \in S $ and an edge $ v_i v_j \in E $ between vertices $ v_i, v_j \in V $ if the corresponding edges $ s_i, s_j \in S $ intersect in $ \Gamma $. 
We also denote the segment in $S$ corresponding to a vertex $v \in V$ by $s(v)$.
Observe that the intersection graph $ C $ of a $ k $-plane drawing $ \Gamma $ has maximum degree $ k $.  
%
Using a standard sweep-line algorithm, computing the intersection graph $C$ of a set of $m$ line segments takes $O(m \log m + |E|)$ time~\cite{bcko-cgaa-08}, where $|E|$ is  the number of intersections.

@@

%\renewcommand\windowpagestuff{%
%	\includegraphics{Reduction_visual}
%	\captionof{figure}{Example of three variable gadgets and\\ a satisfied clause gadget. Dotted parts do not belong\\ to the SPED.}
%	\label{fig:gadget_connection}
%}
%\opencutleft
\begin{proof}
%		\begin{cutout}{2}{0pt}{0.44\textwidth}{15}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$ that has a vertex for each variable $x_i$ placed on a horizontal line and a vertex for each clause $c_j$ either above or below the horizontal line and connected on that side of the line to the three variables appearing in $c_j$. 
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.
%		\end{cutout}

@@

	Each variable gadget is a cycle of segment pairs, with at least one pair for each occurence of the variable in $\phi$, see Fig.~\ref{fig:gadget_connection}. 
	Observe that this cycle has exactly two ink-maximal SPEDs: either all red edges are full segments and all green edges are length-1 stubs or vice versa.
	We associate the configuration with green stubs and full red segments with the value \emph{true} and the configuration with full green segments and red stubs with the value \emph{false}.

@@

%\begin{align*}
\[	
	\solshort(u) = \max\{T_1(u),\dots,T_{i_p}(u)\} \qquad

@@

\]
%\end{align*}

@@

	\bibitem{bkl-us-15}
	Till Bruckdorfer, Michael Kaufmann, and Simon Leibßle.
	\newblock Ped user study.
	\newblock In {\em Graph Drawing (GD'15)}, volume 9411 of {\em LNCS}, pages
	551--553. Springer International Publishing, 2015.

>>>>

The \emph{intersection graph} $ C = (V,E) $ of $ \Gamma $ is the graph containing a vertex $v_i$ in $ V $ for every $ s_i \in S $ and an edge $ v_i v_j \in E $ between vertices $ v_i, v_j \in V $ if the corresponding edges $ s_i, s_j \in S $ intersect in $ \Gamma $. 
We also denote the segment in $S$ corresponding to a vertex $v \in V$ by $s(v)$.
Observe that the intersection graph $ C $ of a $ k $-plane drawing $ \Gamma $ has maximum degree~$ k $.  
%
Using a standard sweep-line algorithm, computing the intersection graph $C$ of a set of $m$ line segments takes $O(m \log m + |E|)$ time~\cite{bcko-cgaa-08}, where $|E|$ is  the number of intersections.

@@

%\renewcommand\windowpagestuff{%
%	\includegraphics{Reduction_visual}
%	\captionof{figure}{Example of three variable gadgets and\\ a satisfied clause gadget. Dotted parts do not belong\\ to the SPED.}
%	\label{fig:gadget_connection}
%}
%\opencutleft
\begin{proof}
%		\begin{cutout}{2}{0pt}{0.44\textwidth}{15}
	We reduce from the \NP-hard problem \ppsat~\cite{l-pftu-82} using similar ideas as in Bruckdorfer's general proof of the hardness of \maxsped~\cite{b-sgh-15}. %, which reduces from the more restricted problem \textsc{Planar Positive 1-in-3 Sat}. 
	Let $\phi$ be a planar 3-Sat formula with $n$ variables $\{x_1, \dots, x_n\}$ and $m$ clauses $\{c_1, \dots, c_m\}$, each consisting of three literals.
	We can assume that $\phi$ comes with a planar drawing of its variable-clause graph $H_\phi$ that has a vertex for each variable $x_i$ and a vertex for each clause $c_j$.
	Each clause vertex is connected to the three variables appearing in the clause.
	In the drawing of $H_\phi$ all variable vertices are placed on a horizontal line and the clause vertices connect to the adjacent variable vertices either from above or from below the horizontal line.
	In our gadget-based reduction we mimic the drawing of $H_\phi$ by creating a 3-plane drawing $\Gamma_\phi$ as a set of line segments of uniform length and a value $L$ such that $\Gamma_\phi$ has a SPED with ink at least $L$ if and only if $\phi$ is satisfiable.
	Figure~\ref{fig:gadget_connection} shows a sketch of the gadgets.
%		\end{cutout}

@@

	Each variable gadget is a cycle of segment pairs, with at least one pair for each occurrence of the variable in $\phi$, see Fig.~\ref{fig:gadget_connection}. 
	Observe that this cycle has exactly two ink-maximal SPEDs: either all red edges are full segments and all green edges are length-1 stubs or vice versa.
	We associate the configuration with green stubs and full red segments with the value \emph{true} and the configuration with full green segments and red stubs with the value \emph{false}.

@@

%\[	
	\solshort(u) = \max\{T_1(u),\dots,T_{i_p}(u)\}\\ % \qquad

@@

%\]

@@

	\bibitem{bkl-us-15}
	Till Bruckdorfer, Michael Kaufmann, and Simon Leibßle.
	\newblock PED user study.
	\newblock In {\em Graph Drawing (GD'15)}, volume 9411 of {\em LNCS}, pages
	551--553. Springer, 2015.
